---
title: "Task_1"
output: html_document
---


# Task 1: Pollutants in the air in the United States

### Picture 1: Air Quality ternds show clean air progress

Emissions of key air pollutants continue to decline from 1990 levels:

* Carbon Monoxide (CO) **decrease 70%**
* Ammonia (NH3) **decrease  8%**
* Nitrogen Oxides (NOx) **decrease 68%**
* Direct Particulate Matter 2.5 microns (PM2.5) **decrease 38%**
* Direct Particulate Matter 10 microns (PM10) **decrease 31%**
* Sulfur Dioxide (SO2) **decrease 92%**
* Volatile Organic Compounds (VOC) **decrease 48%**

### picture 2: Emission Sources Helps Control Air Pollution

Generally, emissions of air pollution come from

* stationary fuel combustion sources (like: electric utilities, industrial boilers)
* industrial and other processes (like: metal smelters, petroleum refineries, cement kilns and dry cleaners)
* highway vehicles
* non-road mobile sources (like: marine vessels, aircraft and locomotives)
As the chart shows, pollutants are emitted by a variety of sources. 

```{r}
library(shiny)
library(readr)
library(highcharter)
library(dplyr)
data <- read_csv("naaqs-emissions-totals-data.csv")
new_data <- read_csv("new.csv")
plotdata<-data
# Define UI for app that draws a histogram ----
ui <- fluidPage(

  # App title ----
  # titlePanel("Economic and pollutant emissions"),

  # Sidebar layout with input and output definitions ----
  sidebarLayout(

    # Sidebar panel for inputs ----
    sidebarPanel(
        h3(strong("Variable introduction")),
        h4(strong("Plot 1 & Plot 2:")),
        br(strong("CO"),": Carbon Monoxide"),
        br(strong("NH3"),": Ammonia"),
        br(strong("NOx"),": Nitrogen Oxides"),
        br(strong("PM2.5"),": Direct Particulate Matter 2.5 microns"),
        br(strong("PM10"),": Direct Particulate Matter 10 microns"),
        br(strong("SO2"),": Sulfur Dioxide"),
        br(strong("VOC"),": Volatile Organic Compounds"),
        br(),
        br(),
        h4(strong("Plot 2:")),
        br(strong("Highway Vehicles"),": car..."),
        br(strong("Industrial and other process"),": metal smelters, petroleum refineries, cement kilns and dry cleaners..."),
        br(strong("Non-Road Mobile"),": marine vessels, aircraft and locomotives..."),
        br(strong("Stationary Fuel Combustion"),": electric utilities, industrial boilers...")
    ),
    
    # Main panel for displaying outputs ----
    mainPanel(
      h2("Air Quality ternds show clean air progress"),
      p("Emissions of key air pollutants continue to decline from 1990 levels:"),
      br(),
      p("Carbon Monoxide (CO) decrease 70%;"),
      br(),
      p("Ammonia (NH3) decrease  8%;"),
      br(),
      p("Nitrogen Oxides (NOx) decrease 68%;"),
      br(),
      p("Direct Particulate Matter 2.5 microns (PM2.5) decrease 38%;"),
      br(),
      p("Direct Particulate Matter 10 microns (PM10) decrease 31%;"),
      br(),
      p("Sulfur Dioxide (SO2) decrease 92%;"),
      br(),
      p("Volatile Organic Compounds (VOC) decrease 48%;"),
      br(),
      highchartOutput("LinePlot"),
      
      h2("American National Emissions By Source Category"),
      p("Generally, emissions of air pollution come from: stationary fuel combustion sources (like: electric utilities, industrial boilers), industrial and other processes (like: metal smelters, petroleum refineries, cement kilns and dry cleaners), highway vehicles, non-road mobile sources (like: marine vessels, aircraft and locomotives) "),
      br(),
      p("As the chart shows, pollutants are emitted by a variety of sources."),
      highchartOutput("percent_hist")
    )
  )
)
```


```{r}
# Define server logic required to draw a histogram ----
server <- function(input, output) {
  # Declining National Air Pollutant Concentration Averages
  # plot a line chart with Double ordinate to show the American declining national air pollutant emissions
    output$LinePlot <- renderHighchart({
      highchart() %>%
      hc_title(text = 'American Declining National Air Pollutant Emissions')%>%
      hc_subtitle(text = "1990 — 2020",
                  style = list(color = "#2b908f", 
                               fontWeight = "bold")) %>% 
      hc_xAxis(categories = plotdata$year)%>%
      hc_yAxis_multiples(
      list(lineWidth = 3,
           title = list(text = "Emissions Excluding CO (Million Tons)")),
      list(showLastLabel = FALSE, opposite = TRUE,
           title = list(text = "CO Emissions (Million Tons)"))
      ) %>% 
      hc_add_series(name = "CO", 
                      data = plotdata$CO,type = "spline", yAxis = 1)%>%
      hc_add_series(name = "NH3", 
                      data = plotdata$NH3,type = "spline")%>%
      hc_add_series(name = "NOx", 
                      data = plotdata$NOx,type = "spline")%>%
      hc_add_series(name = "Direct PM2.5", 
                      data = plotdata$'Direct PM2.5',type = "spline")%>%
      hc_add_series(name = "Direct PM10", 
                      data = plotdata$'Direct PM10',type = "spline")%>%
      hc_add_series(name = "SO2", 
                      data = plotdata$SO2,type = "spline")%>%
      hc_add_series(name = "VOC", 
                      data = plotdata$VOC,type = "spline") %>%
      hc_tooltip(table = TRUE,
                  sort = TRUE,
                  pointFormat = paste0( '<br> <span style="color:{point.color}">\u25CF</span>',"     <b>{series.name}:</b> {point.y} Million Tons"),
                  headerFormat = '<span style="font-size: 13px"><b>Year:</b> {point.key}</span>')
    })
  
  # A bar chart to show American national emissions by source category
  # National Emissions by source category
  output$percent_hist <- renderHighchart({
    hchart(new_data,"column",hcaes(x= "Categories",y = "value",group = "target")) %>%  
    hc_plotOptions(column= list(stacking = "percent"))%>%
    hc_title(text = 'American National Emissions By Source Category')%>%
      hc_yAxis_multiples(
      list(lineWidth = 3,
          title = list(text = "Emissions (%)")))%>%
    hc_xAxis(title = list(text = " "))
  })
}
```

```{r}
shinyApp(ui = ui, server = server)
```